Fast, Scalable Phrase-Based SMT Decoding

### 2016-05-08 acl.2016/acl2016.tex
changes

This contrast with Moses where speed increases to approximately 16 threads but then actually become slower thereafter, Figure~\ref{fig:moses-speed}.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{moses-scalability.png}} 
\end{tabular}
\caption{Moses' decoding speed}
\label{fig:moses-speed}
\end{figure}

@@

>>>>

This contrast with Moses where speed increases to approximately 16 threads but then actually become slower thereafter, Figure~\ref{fig:moses-speed}. Using the tcmalloc library has a small positive effect on decoding speed but does little to improve scalability 
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{moses-scalability.png}} 
\end{tabular}
\caption{Moses' decoding speed}
\label{fig:moses-speed}
\end{figure}

@@

It has been suggested that using a larger language model would overpower the improvements in decoding speed. We tested this posit by replacing the language model in our ar-en experiment with a 96GB language model. Results show that the decoding speed compared to Moses is less than with a smaller language model, Figure~\ref{fig:large-lm}, however, our work still scales monotonically until all CPUs are saturated, unlike Moses.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{large-lm.png}} 
\end{tabular}
\caption{Decoding speed with a large language model}
\label{fig:large-lm}
\end{figure}
